### 2021-08-18 PrevAdjSurvey.tex
Updates from Overleaf

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{pdflscape}    
%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}

@@

\usepackage{graphicx}
\graphicspath{ {./figures/} }

@@

Simulation method:

\begin{itemize}
    \item Simulating weights. To simulate \( k \) weights with a coefficient of variation \( v \):
    \begin{itemize}
        \item Sample \( W_i \sim \text{Beta}\left( \frac{1}{v^2} - \frac{1}{kv^2} - \frac{1}{k}, \left( \frac{1}{v^2} - \frac{1}{nk^2} - \frac{1}{k} \right)  (k - 1) \right)\).
        \item By design \( \E W_i = 1 / k \), and  \( \Var W_i = ( v / k )^2  \).
        \item Thus, \( \E \left[ \sum_{i=1}^k w_i \right] = 1\).
        \item Normalize \( w_i^* = \frac{w_i}{\sum_{i=1}^k w_i} \), to guarantee \( \sum_{i=1}^k w_i^* = 1 \).
        \item These \( w_i^* \) should have approximately the desired coefficient of variation.
    \end{itemize}
    \item Selecting weights with non-zero prevalence. Selecting weights with non-zero prevalence is deterministic. 
    \begin{itemize}
        \item First, the proportion of weights with non-zero prevalence is selected. Call this \( a \), where \( 0 < a \leq k \)
        \item Then, the specific weights with non-zero prevalence are selected by 1 of 3 options:
        \begin{itemize}
            \item High weights: the  \( a \) largest weights are selected.
            \item Uniform weights: \( a \) weights are selected such that the ranks of their weights are evenly spaced. Ex: For \( k = 100 \) and \( a = 3 \), the 25th, 50th and 75th largest weights are selected.
            \item Low weights: the  \( a \) smallest weights are selected.
        \end{itemize}
    \end{itemize}
    \item Determining prevalence among weights with non-zero prevalence.
    \begin{itemize}
        \item \( \theta_i \)  for each of the \( a \) weights with non-zero prevalence is \( \beta / \sum_{i=1}^a w_i^{**} \).
        \item Note: in some cases (Low weights and/or high coefficient of variation) it is not possible for the selected weights to provide an overall level of \( \beta \) prevalence. These cases are discarded.
    \end{itemize}
    \item Simulating data.
    \begin{itemize}
        \item \( X_i \sim \text{Binomial}(n_i, \theta_i) \)
    \end{itemize}
\end{itemize}

@@

\begin{enumerate}
    \item \( k = 50 \), \( n_i = 200 \), Total sample size: 10,000. Meant to resemble a scenario like taking an equal-sized sample from each of the 50 US States.
    \item \( k = 8000 \), \( n_i = 1 \), Total sample size: 8,000. Meant to resemble a scenario with a complex weighting scheme where each person has their own weight.
\end{enumerate}

\begin{landscape}
\begin{figure}
    \centering
    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
    \caption{Dirichlet Weights Scenario 2}
    \label{fig:dws2}
\end{figure}
\end{landscape}
\pagebreak

>>>>

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{pdfpages}
%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}

@@

\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage[colorinlistoftodos]{todonotes}

@@

Simulation method:
In this simulation \( \beta = 0.005 \).
\begin{itemize}
    \item Simulating weights. To simulate \( k \) weights with a coefficient of variation \( v \):
    \begin{itemize}
        \item Sample \( W_i \sim \text{Beta}\left( \frac{1}{v^2} - \frac{1}{kv^2} - \frac{1}{k}, \left( \frac{1}{v^2} - \frac{1}{nk^2} - \frac{1}{k} \right)  (k - 1) \right)\).
        \item By design \( \E W_i = 1 / k \), and  \( \Var W_i = ( v / k )^2  \).
        \item Thus, \( \E \left[ \sum_{i=1}^k w_i \right] = 1\).
        \item Normalize \( w_i^* = \frac{w_i}{\sum_{i=1}^k w_i} \), to guarantee \( \sum_{i=1}^k w_i^* = 1 \).
        \item These \( w_i^* \) should have approximately the desired coefficient of variation.
    \end{itemize}
    \item Selecting weights with non-zero prevalence. Selecting weights with non-zero prevalence is deterministic. 
    \begin{itemize}
        \item First, the proportion of weights with non-zero prevalence is selected. Call this \( a \), where \( 0 < a \leq k \)
        \item Then, the specific weights with non-zero prevalence are selected by 1 of 3 options:
        \begin{itemize}
            \item High weights: the  \( a \) largest weights are selected.
            \item Uniform weights: \( a \) weights are selected such that the ranks of their weights are evenly spaced. Ex: For \( k = 100 \) and \( a = 3 \), the 25th, 50th and 75th largest weights are selected.
            \item Low weights: the  \( a \) smallest weights are selected.
        \end{itemize}
    \end{itemize}
    \item Determining prevalence among weights with non-zero prevalence.
    \begin{itemize}
        \item \( \theta_i \)  for each of the \( a \) weights with non-zero prevalence is \( \beta / \sum_{i=1}^a w_i^{**} \).
        \item Note: in some cases (Low weights and/or high coefficient of variation) it is not possible for the selected weights to provide an overall level of \( \beta \) prevalence. These cases are discarded.
    \end{itemize}
    \item Simulating data.
    \begin{itemize}
        \item \( X_i \sim \text{Binomial}(n_i, \theta_i) \)
    \end{itemize}
\end{itemize}

@@

\begin{enumerate}
    \item Scenario 1. \( k = 50 \), \( n_i = 200 \), Total sample size: 10,000. Meant to resemble a scenario like taking an equal-sized sample from each of the 50 US States.
    \item Scenario 2. \( k = 8000 \), \( n_i = 1 \), Total sample size: 8,000. Meant to resemble a scenario with a complex weighting scheme where each person has their own weight.
\end{enumerate}

Results are presented on the next two pages.
\todo[inline]{Would like to make these figures smaller / more focused. Maybe we don't need to present all of the ``Weights with Non-0 Prevalence."}
\todo[inline]{Maybe need to simulate prevalence \( > 0.005 \) to show wsPoisson failing}
\begin{itemize}
    \item Regardless of the scenario, the two wsPoisson methods achieve at least the desired coverage. This coverage increases as the coefficient of variation among the weights increases.
    \item Regardless of the scenario, when the coefficient of variation among the weights is near 0, all methods perform well.
    \item Regardless of the scenario, when the prevalence is concentrated among the largest weights, increasing coefficient of variation among the weights results in lower coverage for the Agresti-Coull and Clopper-Pearson methods. 
    \item Regardless of the scenario, when the prevalence is concentrated among the smallest weights, increasing coefficient of variation among the weights results in higher coverage for all methods.
    \item When the prevalence is distributed uniformly among the weights, Scenario 1 exhibits similar behavior to when the prevalence is concentrated among the smallest weights.
    \items When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.

\end{itemize}

\begin{landscape}
\includepdf[angle=90]{coverage_50}
\end{landscape}

\begin{landscape}
\includepdf[angle=90]{coverage_8000}
\end{landscape}
